Ripples in the Flow: \\ Fast, General Parameter Estimation with Normalizing Flows and Differentiable Waveforms

### 2023-01-05 src/tex/ms.tex
merging

\definecolor{rb4}{HTML}{27408B}
\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
\newcommand{\flatiron}{\affiliation{Center for Computational Astrophysics,
Flatiron Institute, New York, NY 10010, USA}}
\newcommand{\jhu}{\affiliation{Department of Physics and Astronomy, Johns Hopkins University,
3400 N. Charles Street, Baltimore, Maryland 21218, USA}}

@@

% Title
\title{Turbo fast no compromise gravitational wave parameter estimation}

@@

\author{Thomas Edward}
\jhu

>>>>

\definecolor{rb4}{HTML}{27408B}
\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}
\newcommand{\flatiron}{\affiliation{Center for Computational Astrophysics,
Flatiron Institute, New York, NY 10010, USA}}
\newcommand{\jhu}{\affiliation{William H. Miller III Department of Physics and Astronomy, Johns Hopkins University, Baltimore, Maryland 21218, USA}}

@@

% Title
% \title{Turbo fast no compromise gravitational wave parameter estimation}
% Title Options
\title{Ripples in the Flow: \\ Fast, General Parameter Estimation with Normalizing Flows and Differentiable Waveforms}

@@

\author{Thomas D. P. Edwards}
\jhu
